---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# deeplr

The DeepL Translator made headlines for providing better translations than Google etc. ```deeplr``` is a quick & dirty coded package that contains a singular function - ```translate()``` - that accesses the unofficial DeepL API. Since it is not based on an official API it may stop to function at any time.

I was inspired by the [translateR package](https://github.com/ChristopherLucas/translateR) and relied on some code provided by [Grzegorz Kulikowski](https://psvmware.wordpress.com/2017/09/11/get-deepltranslation-translating-straight-from-your-powershell/) and [this blog post](https://itsalocke.com/blog/r-quick-tip-microsoft-cognitive-services-text-analytics-api/) to figure out how to extract information from the "API" in R. 



## Installation: How do I get it?

```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
# Development version
# install.packages("devtools")
devtools::install_github("paulcbauer/deeplr")
```

## Example: How do I use it?

You can feed ```translate()``` with a character vector or a dataframe. 

```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
# Translate a single string
  dat <- "Essentially, all models are wrong, but some are useful."
  translate(dataset = dat)

# Translate a character vector
  dat <- c("The only way to find out what happens when a complex system is disturbed, is to disturb the system, not merely observe it passively.", 
           "The whole problem with the world is that fools and fanatics are always so certain of themselves, but wiser people are so full of doubts.")
  translate(dataset = dat)

# Translate a column in a dataframe
  library(translateR)
  data(enron)
  translate(dataset = enron,
            column.name = "email")
```


## Next steps
* Increase efficiency of code
* Add option to output multiple languages
* Test robustness.. encoding issues etc.
