---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# deeplr

The DeepL Translator made headlines for providing better translations than Google etc. ```deeplr``` is a quick & dirty coded package that contains a singular function - ```translate()``` - that accesses the unofficial DeepL API. Since it is not based on an official API it may stop to function at any time.

I was inspired by the [translateR package](https://github.com/ChristopherLucas/translateR) and relied on some code provided by [Grzegorz Kulikowski](https://psvmware.wordpress.com/2017/09/11/get-deepltranslation-translating-straight-from-your-powershell/) and [this blog post](https://itsalocke.com/blog/r-quick-tip-microsoft-cognitive-services-text-analytics-api/) to figure out how to extract information from the "API" in R. 



## Installation: How do I get it?

```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
# Development version
# install.packages("devtools")
devtools::install_github("paulcbauer/deeplr")
```

## Example: How do I use it?

You can feed ```translate()``` with a character vector or a dataframe. 

```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
# Load the package
  library(deeplr)

# Translate a single string
  dat <- "Essentially, all models are wrong, but some are useful"
  translate(dataset = dat)

# Translate a character vector
  dat <- c("The only way to find out what happens is to disturb the system",
           "The whole problem with the world is that fools are always so certain of themselves")
  translate(dataset = dat)

# Translate a column in a dataframe
  dat <- data.frame(text = c("The only way to find out what happens is to disturb the system",
           "The whole problem with the world is that fools are always so certain of themselves"))
  translate(dataset = dat, column.name = "text", source.lang = "EN", target.lang = "ES")


  swiss$country <- rownames(swiss)
  translate(dataset = swiss, column.name = "country", source.lang = "FR", target.lang = "EN")
  # well...
```


## Next steps
* Increase efficiency of code
* Add option to output multiple languages
* Test robustness.. encoding issues etc.
